---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

[![Travis-CI Build Status](https://travis-ci.org/r-gris/sfdct.svg?branch=master)](https://travis-ci.org/r-gris/sfdct)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/r-gris/sfdct?branch=master&svg=true)](https://ci.appveyor.com/project/r-gris/sfdct)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/sfdct)](https://cran.r-project.org/package=sfdct)


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# sfdct

The goal of sfdct is to provide constrained triangulations of simple features. 

## Example

This is a basic example which shows you how to decompose a MULTIPOLYGON `sf` data frame object into a GEOMETRYCOLLECTION `sf` data frame object made of triangles:

```{r example}
library(sf)
library(sfdct)
nc <- st_read(system.file("shape/nc.shp", package="sf"))
(nc_triangles <- ct_triangulate(nc[1:5, c("NAME")]))

(asub <- st_geometry(nc_triangles)[[4]] )

plot(asub, col = "aliceblue")



```
See the vignettes for more examples. 



Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
