---
title: "Constrained triangulation for Simple Features"
author: "Michael D. Sumner"
date: "`r Sys.Date()`"
output:
  rmarkdown::html_vignette:
    fig_width: 7
    fig_height: 7
vignette: >
  %\VignetteIndexEntry{constrained-triangulation-simple-features}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Example

This is a basic example which shows you how to decompose a MULTIPOLYGON `sf` data frame object into a GEOMETRYCOLLECTION `sf` data frame object made of triangles:

```{r example}
library(sf)
library(sfct)
nc <- st_read(system.file("shape/nc.shp", package="sf"))
nc_triangles <- ct_triangulate(nc)
plot(nc_triangles[, c("PERIMETER", "NAME")])
```

We can use the underlying `RTriangle::triangulate` arguments to hone the triangles we get. 

```{r hone}
i_feature <- 25
nc1 <- nc[c(i_feature, unlist(st_touches(nc[i_feature, ], nc))), ]
plot(nc1[, c("AREA", "NAME")])

## subvert st_area because we really don't want m^2
st_crs(nc1) <- NA
areas <- st_area(nc1)
st_crs(nc1) <- st_crs(nc)
nc1_triangles <- ct_triangulate(nc1, a = min(areas)/5)
plot(nc1_triangles[, c("AREA", "NAME")])

nc2_triangles <- ct_triangulate(nc1, a = min(st_area(nc1))/25)
plot(nc2_triangles[, c("AREA", "NAME")])

```

Get a grouped triangulated set from a MULTIPOINT. Note how these aren't constrained by 
the edges of the input polygons (because we threw those away!) but these are controlled to have a smaller maximum area. 

Area is calculated in the native coordinates, assuming "planar coordinates", with no respect to the real world. 

```{r MULTIPOINT}
mtriangs <- ct_triangulate(st_cast(nc1, "MULTIPOINT"), a = 0.001)
plot(mtriangs[, 1], col = viridisLite::viridis(nrow(mtriangs)))
```

